Hedonic House Prisce Model King County

### 2023-11-14 Msb205/Msb205kopi.Rmd
:D

```{r Legge inn datasett. Dette fikk jeg ikke lastet ned som dbf-fil}
acs_b19101_familyincome <- read.csv("./Data/acs_b19101_familyincome.csv")
```

@@

```{r}
acs_b19101_familyincome$GEO_ID_TRT <- as.character(acs_b19101_familyincome$GEO_ID_TRT) #må være samme type

WADOH_King_County <- WADOH_King_County %>%
  left_join(acs_b19101_familyincome, 
            by = c("GEO_ID_TRT", "TRACT_LBL"))
```

@@

```{r Laste ned kart}
file_path2 <- "Data/Kart/tracts10.shp"
tracts10 <- st_read(file_path2) #Les inn .shp-filen.
```

```{r endre EPSG}
tracts10 <- st_transform(tracts10, 2926)
```

```{r etnisitet inn i WADOH_K_C}
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT) #til character
WADOH_King_County <- WADOH_King_County %>%
  left_join(acs_b02001_race, by = "GEO_ID_TRT", "TRACT_LBL")
```

```{r Legg census-tracts til?}
tracts10 <- tracts10 %>%
  st_join(WADOH_King_County, by = "GEO_ID_TRT") #Legg census-tract data til kartet
```

@@

```{r}
# Performing the spatial join
joined_data <- st_join(kc_house_data_oppg1, tracts10, by = "GEO_ID_TRT")

# Removing rows with missing values
cleaned_data <- na.omit(joined_data)

@@

```{r}
# Performing the spatial join
joined_data <- st_join(kc_house_data_oppg1, tracts10, by = "GEO_ID_TRT")

# Removing rows with missing values
cleaned_data <- na.omit(joined_data)

# Transforming to EPSG:2926
husdata <- st_transform(cleaned_data, crs = 2926)

@@

## Hus data WADOH K_C (opg3)

#### I)

```{r}
summary.data.frame(tracts10)
```

```{r}
# Performing the spatial join
joined_data <- st_join(husdata, tracts10)

```{r}
# To view the column names of tracts10
names(tracts10)
view(tracts10)
```

#### II)

```{r}
# Filtering out rows with missing values in Shape_area
KC_tracts10 <- tracts10 %>%
  filter(!is.na(Shape_area))
view(KC_tracts10)
```

```{r}
# Adjust the filtering criteria 'WADOH' county, useing COUNTY_STR
wadoh_data <- tracts10 %>%
  filter(COUNTY_STR.x == "033") %>%
  select(TRACT_AREA.x)

####

```{r}
# Renaming the Date column to year_month
cleaned_data <- cleaned_data %>%
  rename(year_month = date)
#view(cleaned_data)
```

```{r}
#Lag en faktor-variabel av år og måned ut fra Date, kall den year_month.
kc_house_data <- cleaned_data %>%
  mutate(year_month = str_c(year, month))
#view(kc_house_data)
```

```{r}
#Lagre .gpkg filen for husdataene . (Sett opsjonen append=FALSE. Ellers får dere ikke lov til å overskrive filen.)
st_write(kc_house_data, "kc_house_data.gpkg", append = FALSE)
st_write(wadoh_data, "wadoh.gpkg", append = FALSE)

>>>>

```{r Legge inn datasett. Dette fikk jeg ikke lastet ned som dbf-fil}
acs_b19101_familyincome <- read.csv("./Data/acs_b19101_familyincome.csv")
acs_b19101_familyincome <- acs_b19101_familyincome %>% 
  select(GEO_ID_TRT)

@@

```{r}
acs_b19101_familyincome$GEO_ID_TRT <- as.character(acs_b19101_familyincome$GEO_ID_TRT) #må være samme type
```

@@

```{r Laste ned kart}
file_path2 <- "Data/Kart/tracts10.shp"
tracts10 <- st_read(file_path2) #Les inn .shp-filen.
view(tracts10)
```

```{r etnisitet inn i WADOH_K_C}
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT) #til character
WADOH_King_County <- WADOH_King_County %>%
  left_join(acs_b02001_race, by = "GEO_ID_TRT")
```

@@

## 3. Hus data

```{r}
library(dplyr)

# Convert the joining key in both dataframes to the same type if they are different
# For example, if GEO_ID_TRT is numeric in one and character in the other:
acs_b02001_race$GEO_ID_TRT <- as.character(acs_b02001_race$GEO_ID_TRT)
acs_b19101_familyincome$GEO_ID_TRT <- as.character(acs_b19101_familyincome$GEO_ID_TRT)

# Now join the datasets
joined_data <- acs_b02001_race %>%
               left_join(acs_b19101_familyincome, by = "GEO_ID_TRT")

# Removing rows with missing values
husdata <- na.omit(joined_data)

# Viewing the data
View(husdata)

@@

## WADOH K_C

```{r}
# Adjust the filtering criteria 'WADOH' county, useing COUNTY_STR
wadoh_data <- husdata %>%
  filter(COUNTY_STR == "033") %>%
  select(TRACT_AREA)

```{r}
# Renaming the Date column to year_month
wadoh_data <- wadoh_data %>%
  rename(year_month = date)
#view(wadoh)
```

```{r}
#Lagre .gpkg filen for husdataene . (Sett opsjonen append=FALSE. Ellers får dere ikke lov til å overskrive filen.)
st_write(husdata, "husdata.gpkg", append = FALSE)
st_write(wadoh_data, "wadoh.gpkg", append = FALSE)

@@

```{r}
